Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-01-25 paper.tex
Add annotated figure.
Make one submittable version.

\author{
	\IEEEauthorblockN{
		\textcolor{blue}{Praveen Venkatesh %\IEEEauthorrefmark{1}
		and Pulkit Grover} %\IEEEauthorrefmark{2}
	}
	%\IEEEauthorblockA{
	%    Electrical \& Computer Engineering,
	%    and the Center for the Neural Basis of Cognition,
	%    Carnegie Mellon University
	%    \\
	%    \IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
	%    \IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	%}
}

@@

We give lower bounds on the minimax risk (mean squared-error in location) in
estimating the location of the source, which apply to all estimators, for
\textcolor{blue}{certain classes of diffusive media represented by low-pass
filters}, when using a unformly distributed sensor array. We show that
\textcolor{blue}{for sensors of a fixed size}, the lower bound decays with
increasing numbers of sensors. We also perform a preliminary numerical analysis
to understand the effect of increasing the number of sensors to infinity by
shrinking their size, wherein the bound saturates for large sensor numbers.
\textcolor{blue}{In the second scenario, it is seen that there is greater
benefit to increasing the number of sensors} as the signal-to-noise increases.
Our bounds are the first to give a scaling for the minimax risk in terms of the
number of sensors used.

@@

%- The source localization problem is one that occurs in several fields
%  - Brain activity measurement, in the form of localizing brain activity
%    - Possible applications are epilepsy focus localization
%    - Neuroscientific experiments - locating the source of activity at certain
%      points in time, for understanding brain function
%  - Need to read Vetterli's papers on acoustic source localization-type things
%  - Need to read up linear inverse problems literature

%- Previous work
%  - In the brain activity localization side of things, lots of algorithms, but
%    not much understanding of bounds (Mosher, Grover).
%    - These have their own issues: CRLB does not apply to all estimators, info
%      theoretic bound does not give scaling with sensors
%  - Other work on minimax bounds and estimators for linear inverse problems
%    concentrate on function estimation (with smoothness constraints on the
%    function being estimated)
%    - e.g. Tsybakov, Efromovich, Ibragimov \& Has'minskii, and references
%      therein
%    - Obviously, bounds for function estimation will look radically different
%      from bounds for a location parameter
%    - Location-parameter based work appears to exist in Ibragimov-Has'minskii,
%      but they treat it as an exercise, without seriously considering
%      extensions, and looking at scaling with number of sensors

%- Cite Fisher's book on circular domain signals somewhere (statistical analysis
%  of circular data)

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well, \textcolor{red}{such
	as auditory localization of a sound using a microphone array (although
	typically, very different approaches are employed there, when compared to
EEG source localization) <shall I remove this?>}. A vast literature on linear
inverse problems and deconvolution algorithms exists
(see~\cite{Bal2012Introduction} for an introduction to this field), and has
addressed the reduced one-dimensional problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point
source~\cite{Cavalier2002Sharp}. \textcolor{blue}{The error metric used when
recovering the whole function is the mean-squared error in the space of
square-integrable functions, rather than the distance between the true and
estimated locations}. Work that \emph{does} address point sources and
location-based error metrics~\cite{Ibragimov1981Statistical} does not, to our
knowledge, address scaling in the number of sensors.

Hence, we believe that this paper is the first to give lower bounds on source
localization error (measured in an $\ell_2$-distance sense) in estimating the
location of a one-dimensional point source, which is observed by sensors
through a diffusive medium (treated as a low-pass filter), and corrupted by
additive white Gaussian noise. We describe the problem setting in detail in
Section~\ref{sec:source-localization} and the minimax techniques and our main
results \textcolor{blue}{(for a naive and then for a more physical sensor
model)} in Section~\ref{sec:minimax-lower-bounds}. We conclude in
Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
and on how our results can be extended to other simple settings.

\textcolor{blue}{
For EEG source localization, we hope to find algorithms that achieve scalings
close to the bounds we present.  We also expect to build upon the techniques
presented in this paper to derive bounds for spherical and realistic brain
models.
}

@@

The sensors sample the shifted continuous-space impulse response, with some
additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
the $m$-length vector $\v x(\theta)$:
\begin{equation} \label{eq:sampled-signal}
	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)S}{m}; \theta\Big)\bigg]^T
\end{equation}
where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
additive noise is given by $\v \epsilon$ (to be described shortly), and the
noisy samples are represented by
\begin{equation} \label{eq:sensor-obs}
	\v y = \v x(\theta) + \v \epsilon.
\end{equation}
In the source localization problem, we receive $n$ trials\footnote{The word
``trials'' comes from neuroscience literature, where several trials of an
experiment are run with a single participant. The participant is given the same
stimulus in each trial, evoking the same response in the brain (usually with
some trial-to-trial variability). For our purposes, we assume that trials are
effectively i.i.d. realizations of sensor noise, with no trial-to-trial
variability.} (i.e., $n$ realizations) of $\v y$ according to
equation~\eqref{eq:sensor-obs}, for the same point source $\theta$, using which
we need to estimate the location of the source.
The complete signal model described in this section is summarized in
Fig.~\ref{fig:signal-model}.

@@

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.5in]{block-diagram}
	\caption{A diagramatic representation of the signal model described in
	section~\ref{sec:signal-model}.}
	\label{fig:signal-model}
\end{figure}

@@

\textcolor{blue}{We start by lower bounding the maximum risk of the estimation problem with the
average risk of a multiple hypothesis testing problem.} For this, we first need
to define a $2\delta$-packing.%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown true hypothesis which takes values uniformly from
	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}. Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be large if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high.

@@

Thus, the final lower bound can be written as:
\begin{equation} \label{eq:le-cam-bound}
	\mathfrak{M}_n(\mathcal P, \Phiorho) \geq \frac{\Phi(\delta)}{2} \big(1 - \norm{P_1^n - P_0^n}_{TV}\big)
\end{equation}
The superscripts ``$n$'' remind us that these are $n$-fold product
distributions, since we have $n$ i.i.d. trials used in the estimate.  The
difficulty in Le Cam's method lies in selecting the two hypotheses to trade-off
the effect due to a small value of $\delta$ and a large value of $\norm{P_1^n -
P_0^n}_{TV}$ appropriately, to derive the tightest possible bound.

@@

The bound in Theorem~\ref{thm:main-lb} may mislead one to think that the error
in source localization goes to zero, as the number of sensors goes to infinity.
\textcolor{blue}{
This observation is qualitatively different from the information-theoretic
lower bound given in~\cite{Grover2016Fundamental}, where even with an infinite
number of sensors, the lower bound is strictly greater than zero. This
indicates that the bound in section~\ref{sec:lecam-lb} is failing to capture
some effect which leads to saturation of error, as the number of sensors
increases.
}

Indeed, the bound in Theorem~\ref{thm:main-lb} assumes that an arbitrarily
large number of sensors can be squeezed into a finite amount of space, and that
these sensors \emph{still} give us i.i.d.\ observations, with the same noise
variance. This is aphysical, since in reality, each sensor has a certain width,
and the value measured by it is the integral of the continuous-space signal
within that width (analogous to a sample-and-hold circuit, which integrates a
continuous-\emph{time} signal over a short period).  If the width of a sensor
is decreased, then effectively, its signal-to-noise ratio reduces.  This is
intuitively evident in the sample-and-hold analogy: to compute the signal
value, the integral must be divided by the time interval over which the
integration is performed; this division amplifies noise as the time interval
gets smaller.

We performed a preliminary study to understand the effect of viewing sensors as
integrators. In the new sensor model, sensors have a width which decreases as
their number grows to infinity. Concretely, the $k$-th sensor which is located
at $s = kS/m$ extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$.
The signal sensed by this sensor is the $k$-th element of $\v x(\theta)$, now
given by
\begin{equation}
	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
\end{equation}
\textcolor{blue}{
The noise vector $\v \epsilon$ is also generated similarly, by integrating over
small sections of a wide-sense-stationary white noise process, which is assumed
to additively corrupt the continuous-space signal $x(s;\theta)$ prior to
sampling. This leads to i.i.d.\ noise values at sensors (since they do not
overlap), with variance inversely proportional to $m$, i.e., $\sigma(m) \propto
1/\sqrt{m}$.
}

The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
admits a solution which gives a bound for all values of $m$. We instead compute
the bound numerically, using exact expressions for error probability in a
binary hypothesis test. For gaussian distributions of equal variance and a
uniform prior on the hypotheses, the minimum possible error probability (over
all tests) is a Q-function in the distance between their
means~\cite{NPLemmaOrSimilar},
\begin{equation}
	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg).
\end{equation}
where $Q(x) = \int_x^\infty \frac{1}{\sqrt{2\pi u}} e^{-u^2/2} du$. Hence, from
Theorem~\ref{thm:est-to-testing},
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
\end{equation}
This bound is valid for any $\{\theta_0, \theta_1\}$ constituting a
$2\delta$-packing of $\Theta$. To numerically optimize over all possible
packings, we relax the process by fixing $\theta_0 = 0$ and optimizing over
$\theta_1 = 2\delta$.  We compute sensor values by performing numerical
integration, and find the best possible $\delta$ by grid search.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=3.2in]{lb-vs-numsensors-int}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location. The different curves are
		for different numbers of ``trials'' $n$ (i.i.d.\ sensor observations).
		The bound saturates for large $m$, indicating that for a fixed number
		of trials (or equivalently, for a fixed SNR), there is reduced benefit
		in increasing the number of sensors beyond a point. However, with more
		trials, the bound saturates at increasingly larger numbers of sensors.
	Thus, there is benefit to increasing the number of sensors, provided SNR
can be increased by leveraging larger numbers of trials.}
	\label{fig:numerical}
\end{figure}

@@

\textcolor{blue}{
Another point on sensor placement bears repeating: the bounds derived in this
paper apply to only a specific sensor configuration, i.e., the uniform one.
Intuitively, this is the correct choice in the minimax setting, since any
non-uniform placement will have one or more points which is far from all
sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
$\theta$ for which the value of the impulse response at the sensors is
smallest, so that the ratio of mean-sensor-value to noise variance (a form of
``SNR'') is minimized.
}

>>>>

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh (\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
		and Pulkit Grover (\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
	}
	%\IEEEauthorblockA{
	%    Electrical \& Computer Engineering,
	%    and the Center for the Neural Basis of Cognition,
	%    Carnegie Mellon University
	%    \\
	%    \IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
	%    \IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	%}
}

@@

We give lower bounds on the minimax risk (mean squared-error in location) in
estimating the location of the source, which apply to all estimators, for
certain classes of diffusive media represented by low-pass
filters, when using a uniformly distributed sensor array. We show that
for sensors of a fixed size, the lower bound decays with
increasing numbers of sensors. We also perform a preliminary numerical analysis
to understand the effect of increasing the number of sensors to infinity by
shrinking their size, wherein the bound saturates for large sensor numbers.
In the second scenario, it is seen that there is greater
benefit to increasing the number of sensors as the signal-to-noise increases.
Our bounds are the first to give a scaling for the minimax risk in terms of the
number of sensors used.

@@

@@

The one-dimensional toy problem is an effective tool for understanding bounds
on source localization accuracy in other settings as well. A vast literature on
linear inverse problems and deconvolution algorithms exists
(see~\cite{Bal2012Introduction} for an introduction to this field), and has
addressed the reduced one-dimensional problem in broad settings
(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
references therein). However, our setting and interpretation appears to be
unique, since most prior work focuses on recovering a whole function (given
certain smoothness constraints), rather than locating a point
source~\cite{Cavalier2002Sharp}. Work that \emph{does} address point sources
and location-based error metrics~\cite{Ibragimov1981Statistical} does not, to
our knowledge, address scaling in the number of sensors.

Hence, we believe that this paper is the first to give lower bounds on source
localization error (measured in an $\ell_2$-distance sense) in estimating the
location of a one-dimensional point source, which is observed by sensors
through a diffusive medium (treated as a low-pass filter), and corrupted by
additive white Gaussian noise. We describe the problem setting in detail in
Section~\ref{sec:source-localization} and the minimax techniques and our main
results (for a naive and then for a more physical sensor model) in
Section~\ref{sec:minimax-lower-bounds}. We conclude in
Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
and on how our results can be extended to other simple settings.

For EEG source localization, we hope to find algorithms that achieve scalings
close to the bounds we present.  We also expect to build upon the techniques
presented in this paper to derive bounds for spherical and realistic brain
models.

@@

The sensors sample the shifted continuous-space impulse response, with some
additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
the $m$-length vector $\v x(\theta)$:
\begin{equation} \label{eq:sampled-signal}
	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)S}{m}; \theta\Big)\bigg]^T
\end{equation}
where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
additive noise is given by $\v \epsilon$ (to be described shortly), and the
noisy samples are represented by
\begin{equation} \label{eq:sensor-obs}
	\v y = \v x(\theta) + \v \epsilon.
\end{equation}
In the source localization problem, we receive $n$ trials\footnote{The word
``trials'' comes from neuroscience literature, where several trials of an
experiment are run with a single participant. The participant is given the same
stimulus in each trial, evoking the same response in the brain (usually with
some trial-to-trial variability). For our purposes, we assume that trials are
effectively i.i.d.\ realizations of sensor noise, with no trial-to-trial
variability.} (i.e., $n$ realizations) of $\v y$ according to
equation~\eqref{eq:sensor-obs}, for the same point source $\theta$, using which
we need to estimate the location of the source.
The complete signal model described in this section is summarized in
Fig.~\ref{fig:signal-model}.

@@

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.5in]{block-diagram}
	\caption{A diagrammatic representation of the signal model described in
	section~\ref{sec:signal-model}.}
	\label{fig:signal-model}
\end{figure}

@@

We start by lower bounding the maximum risk of the estimation problem with the
average risk of a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing.%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if
	\begin{equation}
		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
	\end{equation}
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown true hypothesis which takes values uniformly from
	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}. Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be large if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high.

@@

Thus, the final lower bound can be written as:
\begin{equation} \label{eq:le-cam-bound}
	\mathfrak{M}_n(\mathcal P, \Phiorho) \geq \frac{\Phi(\delta)}{2} \big(1 - \norm{P_1^n - P_0^n}_{TV}\big)
\end{equation}
The superscripts ``$n$'' remind us that these are $n$-fold product
distributions, since we have $n$ i.i.d.\ trials used in the estimate.  The
difficulty in Le Cam's method lies in selecting the two hypotheses to trade-off
the effect due to a small value of $\delta$ and a large value of $\norm{P_1^n -
P_0^n}_{TV}$ appropriately, to derive the tightest possible bound.

@@

The bound in Theorem~\ref{thm:main-lb} may mislead one to think that the error
in source localization goes to zero, as the number of sensors goes to infinity.
This observation is contradicts the information-theoretic lower bound given
in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
the lower bound is strictly greater than zero. This indicates that the bound in
section~\ref{sec:lecam-lb} is failing to capture some effect which leads to
saturation of error as the number of sensors increases.

Indeed, the bound in Theorem~\ref{thm:main-lb} assumes that an arbitrarily
large number of sensors can be squeezed into a finite amount of space, and that
these sensors \emph{still} have the same SNR.  This is aphysical, since in
reality, each sensor has a certain width, and the value measured by it is the
integral of the continuous-space signal within that width (analogous to a
sample-and-hold circuit, which integrates a continuous-\emph{time} signal over
a short period).  If the width of a sensor is decreased, then effectively, its
SNR reduces.  This is intuitively evident in the sample-and-hold analogy: to
compute the signal value, the integral must be divided by the time interval
over which the integration is performed; this division amplifies noise as the
time interval gets smaller.

We performed a preliminary study to understand the effect of viewing sensors as
integrators. In the new sensor model, sensors have a width which decreases as
their number grows to infinity. Concretely, the $k$-th sensor which is located
at $s = kS/m$ extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$.
The signal sensed by this sensor is the $k$-th element of $\v x(\theta)$, now
given by
\begin{equation}
	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
\end{equation}
The noise vector $\v \epsilon$ is also generated similarly, by integrating over
small sections of a white noise process, which is assumed to additively corrupt
the continuous-space signal $x(s;\theta)$ prior to sampling. This leads to
i.i.d.\ noise values at sensors (since they do not overlap), with variance
inversely proportional to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$.

The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
admits a closed-form solution which gives a bound for all values of $m$. We
instead compute the bound numerically, using exact expressions for error
probability in a binary hypothesis test. For Gaussian distributions of equal
variance and a uniform prior on the hypotheses, the minimum possible error
probability (over all tests) is a $Q$-function in the distance between their
means~\cite{NPLemmaOrSimilar},
\begin{equation}
	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg).
\end{equation}
where $Q(x) = \int_x^\infty \frac{1}{\sqrt{2\pi}} e^{-u^2/2} du$. Hence, from
Theorem~\ref{thm:est-to-testing},
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
\end{equation}
This bound is valid for any $\{\theta_0, \theta_1\}$ constituting a
$2\delta$-packing of $\Theta$. To numerically optimize over all possible
packings, we relax the process by fixing $\theta_0 = 0$ and optimizing over
$\theta_1 = 2\delta$.  We compute sensor values by performing numerical
integration, and find the best possible $\delta$ by grid search.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.8in]{lb-vs-m-annotated}
	\caption{A numerically generated plot of the lower bound on minimax risk of
		source localization, against the number of uniformly distributed
		sensors, $m$, used to estimate the location. The different curves are
		for different numbers of ``trials'' $n$ (i.i.d.\ sensor observations).
		The bound saturates for large $m$, indicating that for a fixed number
		of trials (or equivalently, for a fixed SNR), there is reduced benefit
		in increasing the number of sensors beyond a point. However, with more
		trials, the bound saturates at increasingly larger numbers of sensors.
	Thus, there is benefit to increasing the number of sensors, provided SNR
can be increased by leveraging larger numbers of trials.}
	\label{fig:numerical}
\end{figure}

@@

Another point on sensor placement bears repeating: the bounds derived in this
paper apply to only a specific sensor configuration, i.e., the uniform one.
Intuitively, this is the correct choice in the minimax setting, since any
non-uniform placement will have one or more points which is far from all
sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
$\theta$ for which the value of the impulse response at the sensors is
smallest, so that the ratio of mean-sensor-value to noise variance (a form of
SNR) is minimized.
